Intersection of non-matching grids of different dimensions

### 2016-09-28 paper_intersections.tex
Finish introduction (possibly need yet better research on algorithms)

%% main text
\section{Introduction}
Structure:
\begin{itemize}
 \item Introduction of the problem. 
 \item Overview of methods using some sort of mesh intersections.
 \item Our motivation from groundwater applications.
 \item Existing algorithms.
 \item Our contribution:
    new algorithms for element intersections based on \plucker coordinates,
    improvement of the front tracking algorithm
 \item Paper overview   
\end{itemize}

@@

We consider a composed mesh $\mathcal T$ consisting of meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$. 
We assume that the meshes $\mathcal T_i$ are connected, that is the graph having elements for vertices and their nighbouring for edges is connected.
We also assume that no submesh intersect itself. Further we assume that only $\mathcal{T}_1$ have $d_1=3$ and $d_i < 3$ for $i>1$. 
The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
and compute that intersection. Every (possibly degenerated) intersection polygon (IP) is determined by its corners called intersection corners (IC).
For every IC we want to compute its barycentric coordinates on $K$ and on $L$.

The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. Second, compute the intersection for particular pair.
In order to get candidate pairs efficiently, the existing algorithms use either various space trees \cite{massing_efficient_2013} or front tracing
\cite{gander_algorithm_2013} or both \cite{elsheikh_reliable_2012} as in our approach. To compute the actual intersections, we 
use the \plucker coordinates for the line-triangle intersections and a modification of the  Platis and Theoharis algorithm \cite{platis_fast_2003}
for the line-tetrahedron intersections. These are used as the building block for the triangle-triangle and the trinagle-tetrahedron cases.

They suggested a solution, based on \cite{yuan_efficient_2003} for the two aspects of the problem: 
\begin{enumerate}[itemsep=-3pt]
\item an efficient identification of the intersecting pairs of elements,
\item an efficient computation of the actual intersection for the single element pair.
\end{enumerate}
The algorithm is based on the methods used in the computer graphics, in particular for the task (b) \plucker
coordinates are employed to efficiently compute 1D-2D intersection in three-dimensional space.

\begin{figure}[!htb]
  \centering
  \setcounter{subfigure}{0}
  \subfloat[1D-3D]{
    \includegraphics[width=0.3\textwidth]{\figpath intersection_13.pdf} }
  \hspace{10pt}
  \subfloat[2D-3D]{
    \includegraphics[width=0.3\textwidth]{\figpath intersection_23.pdf} }
\end{figure}

For the 1D-3D and 2D-3D cases, the basic algorithm is applied on sides and edges of the simplices and 
all the topological information coming from the performed \plucker products is carefully collected
to obtain final intersecting object.
Further in 2D-3D case, an optimized tracing algorithm is suggested to directly obtain the correct order and 
orientation of the edges of the intersection polygon.

>>>>

%% main text
\section{Introduction}

@@

We consider a composed mesh $\mathcal T$ consisting of simplicial meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$. 
We assume that the meshes $\mathcal T_i$ are connected, that is the graph having elements for vertices and their nighbouring for edges is connected.
We also assume that no submesh intersect itself. Further we assume that only $\mathcal{T}_1$ have $d_1=3$ and $d_i < 3$ for $i>1$. 
The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
and compute that intersection. Every (possibly degenerated) intersection polygon (IP) is determined by its corners called intersection corners (IC).
For every IC we want to compute its barycentric coordinates on $K$ and on $L$.

The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. Second, compute the intersection for particular pair.
In order to get candidate pairs efficiently, the existing algorithms use either various space trees \cite{massing_efficient_2013} or front tracing
\cite{gander_algorithm_2013} or both \cite{elsheikh_reliable_2012} as in our approach. To compute the actual intersections, we 
use the \plucker coordinates for the line-triangle intersections and a modification of the  Platis and Theoharis algorithm \cite{platis_fast_2003}
for the line-tetrahedron intersections. These are used as the building block for the triangle-triangle and the triangle-tetrahedron cases.

\noteJB{Better overview of works, seems that most of works deals with simple intersections, can not find any example of 2d-3d.}

Our contribution is twofold: First, we present family of efficient algorithms based on \plucker coordinates for computing 1d-2d, 1d-3d, 2d-2d, and 2d-3d intersections 
of simplicies. Second, we use the front tracking algorithm both to minimize set of intersection candidates as well to reuse part of calculations made on neighboring
intersections. The paper is organized as follows \dots
